Supporting information - Bayesian regression facilitates quantitative modelling of cell metabolism

### 2024-01-12 paper/main.qmd
update gh action and fix equations

- A measurement model or "likelihood" that probabilistically describes
how likely any possible measurement set is given the true values
of the measured quantities, i.e. a probability density function $l:
\mathfrak{Y}\times\hat{\mathfrak{Y}} \rightarrow [0, 1]$ where $\mathfrak{Y}$
is the set of all possible measurement sets and $\hat{\mathfrak{Y}}$ is the set
of all possible true measurable values.

- A deterministic process model that describes the measured quantities in
terms of unknown, possibly unobserved parameters $\theta$, i.e. a function $d:
\mathfrak{theta} -> \hat{mathfrak{Y}}$.

- A prior model that probabilistically describes how likely any possible set
of parameter values is, without considering any information included in the
measurement model, i.e. a probability density function $\pi : \mathfrak{theta}
\rightarrow [0, 1]$.

Together these components determine a joint probability function
that encapsulates the Bayesian statistical model, i.e. a function $p:
\mathfrak{Y}\times\mathfrak{theta}\rightarrow[0,1]$ such that for any $\theta$
and $y$, $p(\theta, y) = \pi(\theta)l(y\mid\theta)$. Substantive questions about
the implications of the assumptions implicit in the model components can be
formulated in terms of this joint density function.

In particular, questions about what the model implies, given a particular
measurement set $y$ can be formulated in terms of the conditional probability
density function $p_{\mid y}:\mathfrak{theta}\rightarrow[0,1]$. Bayes's
theorem guarantees that this conditional density is proportional to the
product of the prior and likelihood, i.e. $p_{\mid y}(\theta) \propto
\pi(\theta)l(y\mid\theta)$ See [@gelmanBayesianDataAnalysis2020a, Ch 1] for an
extended discussion of the theory of Bayesian statistical inference.

>>>>

- A measurement model or "likelihood" that probabilistically describes
how likely any possible measurement set is given the true values
of the measured quantities, i.e. a probability density function $l:
\mathcal{Y}\times\hat{\mathcal{Y}} \rightarrow [0, 1]$ where $\mathcal{Y}$
is the set of all possible measurement sets and $\hat{\mathcal{Y}}$ is the set
of all possible true measurable values.

- A deterministic process model that describes the measured quantities in
terms of unknown, possibly unobserved parameters $\theta$, i.e. a function $d:
\mathcal{\theta} -> \hat{\mathcal{Y}}$.

- A prior model that probabilistically describes how likely any possible set
of parameter values is, without considering any information included in the
measurement model, i.e. a probability density function $\pi : \mathcal{\theta}
\rightarrow [0, 1]$.

Together these components determine a joint probability function
that encapsulates the Bayesian statistical model, i.e. a function $p:
\mathcal{Y}\times\mathcal{\theta}\rightarrow[0,1]$ such that for any $\theta$
and $y$, $p(\theta, y) = \pi(\theta)l(y\mid\theta)$. Substantive questions about
the implications of the assumptions implicit in the model components can be
formulated in terms of this joint density function.

In particular, questions about what the model implies, given a particular
measurement set $y$ can be formulated in terms of the conditional probability
density function $p_{\mid y}:\mathcal{theta}\rightarrow[0,1]$. Bayes's
theorem guarantees that this conditional density is proportional to the
product of the prior and likelihood, i.e. $p_{\mid y}(\theta) \propto
\pi(\theta)l(y\mid\theta)$ See [@gelmanBayesianDataAnalysis2020a, Ch 1] for an
extended discussion of the theory of Bayesian statistical inference.

### 2024-01-12 paper/main.tex
update gh action and fix equations

\title[]{Bayesian regression facilitates quantitative modelling of cell
metabolism}
\makeatletter
\begin{document}
\maketitle
\begin{abstract}
This paper presents Maud, a command-line application that implements
Bayesian statistical inference for kinetic models of biochemical
metabolic reaction networks. Maud takes into account quantitative
information from omics experiments and background knowledge, as well as
structural information about kinetic mechanisms, regulatory interactions
and enzyme knockouts. Our paper reviews the existing options in this
area, presents a case study illustrating how Maud can be used to analyse
a metabolic network and explains the biological, statistical and
computational design decisions underpinning Maud.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, borderline west={3pt}{0pt}{shadecolor}, breakable, boxrule=0pt, interior hidden, frame hidden, sharp corners]}{\end{tcolorbox}}\fi

@@

\begin{itemize}
\item
  A measurement model or ``likelihood'' that probabilistically describes
  how likely any possible measurement set is given the true values of
  the measured quantities, i.e.~a probability density function
  \(l: \mathfrak{Y}\times\hat{\mathfrak{Y}} \rightarrow [0, 1]\) where
  \(\mathfrak{Y}\) is the set of all possible measurement sets and
  \(\hat{\mathfrak{Y}}\) is the set of all possible true measurable
  values.
\item
  A deterministic process model that describes the measured quantities
  in terms of unknown, possibly unobserved parameters \(\theta\), i.e.~a
  function \(d: \mathfrak{theta} -> \hat{mathfrak{Y}}\).
\item
  A prior model that probabilistically describes how likely any possible
  set of parameter values is, without considering any information
  included in the measurement model, i.e.~a probability density function
  \(\pi : \mathfrak{theta} \rightarrow [0, 1]\).
\end{itemize}

Together these components determine a joint probability function that
encapsulates the Bayesian statistical model, i.e.~a function
\(p: \mathfrak{Y}\times\mathfrak{theta}\rightarrow[0,1]\) such that for
any \(\theta\) and \(y\), \(p(\theta, y) = \pi(\theta)l(y\mid\theta)\).
Substantive questions about the implications of the assumptions implicit
in the model components can be formulated in terms of this joint density
function.

In particular, questions about what the model implies, given a
particular measurement set \(y\) can be formulated in terms of the
conditional probability density function
\(p_{\mid y}:\mathfrak{theta}\rightarrow[0,1]\). Bayes's theorem
guarantees that this conditional density is proportional to the product
of the prior and likelihood,
i.e.~\(p_{\mid y}(\theta) \propto \pi(\theta)l(y\mid\theta)\) See
\citep[Ch 1]{gelmanBayesianDataAnalysis2020a} for an extended discussion
of the theory of Bayesian statistical inference.

>>>>

\title[]{Bayesian regression facilitates quantitative modelling of cell
metabolism}
\makeatletter
\begin{document}
\maketitle
\begin{abstract}
This paper presents Maud, a command-line application that implements
Bayesian statistical inference for kinetic models of biochemical
metabolic reaction networks. Maud takes into account quantitative
information from omics experiments and background knowledge, as well as
structural information about kinetic mechanisms, regulatory interactions
and enzyme knockouts. Our paper reviews the existing options in this
area, presents a case study illustrating how Maud can be used to analyse
a metabolic network and explains the biological, statistical and
computational design decisions underpinning Maud.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, frame hidden, breakable, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, interior hidden, enhanced]}{\end{tcolorbox}}\fi

@@

\begin{itemize}
\item
  A measurement model or ``likelihood'' that probabilistically describes
  how likely any possible measurement set is given the true values of
  the measured quantities, i.e.~a probability density function
  \(l: \mathcal{Y}\times\hat{\mathcal{Y}} \rightarrow [0, 1]\) where
  \(\mathcal{Y}\) is the set of all possible measurement sets and
  \(\hat{\mathcal{Y}}\) is the set of all possible true measurable
  values.
\item
  A deterministic process model that describes the measured quantities
  in terms of unknown, possibly unobserved parameters \(\theta\), i.e.~a
  function \(d: \mathcal{\theta} -> \hat{\mathcal{Y}}\).
\item
  A prior model that probabilistically describes how likely any possible
  set of parameter values is, without considering any information
  included in the measurement model, i.e.~a probability density function
  \(\pi : \mathcal{\theta} \rightarrow [0, 1]\).
\end{itemize}

Together these components determine a joint probability function that
encapsulates the Bayesian statistical model, i.e.~a function
\(p: \mathcal{Y}\times\mathcal{\theta}\rightarrow[0,1]\) such that for
any \(\theta\) and \(y\), \(p(\theta, y) = \pi(\theta)l(y\mid\theta)\).
Substantive questions about the implications of the assumptions implicit
in the model components can be formulated in terms of this joint density
function.

In particular, questions about what the model implies, given a
particular measurement set \(y\) can be formulated in terms of the
conditional probability density function
\(p_{\mid y}:\mathcal{theta}\rightarrow[0,1]\). Bayes's theorem
guarantees that this conditional density is proportional to the product
of the prior and likelihood,
i.e.~\(p_{\mid y}(\theta) \propto \pi(\theta)l(y\mid\theta)\) See
\citep[Ch 1]{gelmanBayesianDataAnalysis2020a} for an extended discussion
of the theory of Bayesian statistical inference.

### 2024-01-12 paper/supporting_information.tex
update gh action and fix equations

\title[]{Supporting information - Bayesian regression facilitates
quantitative modelling of cell metabolism}
\makeatletter
\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, breakable, frame hidden, interior hidden, enhanced, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi

>>>>

\title[]{Supporting information - Bayesian regression facilitates
quantitative modelling of cell metabolism}
\makeatletter
\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, breakable, interior hidden, frame hidden, sharp corners, enhanced, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi
